\thispagestyle{empty}
\def\brule#1{\vrule width#1 height -1.1pt depth 1.5pt\relax}

\markboth{{\sc thesis proposal}}{{\sc thesis proposal}}
\def\titleone{Protecting User Data in Large-Scale Web Services}
\def\author{Frank Wang}
\def\addrone{32 Vassar Street, \#32-G978}
\def\addrtwo{Cambridge, MA  02139}

\def\degree{Doctor of Philosophy}
\def\deptname{Electrical Engineering and Computer Science}
\def\laboratory{Computer Science and Artificial Intelligence
  Laboratory}
%\def\group{Parallel and Distributed Operating Systems Group}

\def\submissiondate{\today}
\def\completiondate{July 2018}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{center}
{\large \sc   
  Massachusetts Institute of Technology
\\ Department of \deptname \\}
\vspace{.2in}
{\large \sc
   Proposal for Thesis Research in Partial Fulfillment
\\ of the Requirements for the Degree of
\\ \degree \\}
\end{center}

\vspace{.3in}

\def\sig{{\small \sc (Signature of Author)}}

\begin{tabular}{r l c}
   {\small \sc Title:}                       & \multicolumn{2}{l}{\titleone} \\
%   							& \multicolumn{2}{l}{\titletwo}
\\ {\small \sc Submitted by:}
                            & \author  & \\
                            & \addrone & \\
                            & \addrtwo & \\  \\
                            & \cline{1-1} \vspace{-0.2in} &  \\

			                & \makebox[1.8in][c]{\sig} & \\
			    
\\ {\small \sc Date of Submission:}          & \multicolumn{2}{l}{\submissiondate}
\\ {\small \sc Expected Date of Completion:} & \multicolumn{2}{l}{\completiondate}
\\ {\small \sc Laboratory:}                  & \multicolumn{2}{l}{\laboratory}
%\\ {\small \sc Group:} & \multicolumn{2}{l}{\group}
\end{tabular}

%
%


\vspace{.3in}
\noindent {\bf \sc Brief Statement of the Problem:}

\noindent \abstract

Web services like Google, Facebook, and Dropbox are now an essential part of people’s lives. Users
willingly provide their data to these services because these services deliver substantial value in return
through their centralization and analysis of data, such product recommendations and ability to easily
share information. To provide this value, 
these services collect, store, and analyze large amounts of their users’ sensitive
data. However, once the user provides her information to the web service, she loses control over how the
application manipulates that data. For example, a user cannot control where the application forwards
her data. Even if the service wanted to allow users to define access controls, it is unclear how these access
controls should be expressed and enforced. Not only is it difficult to develop these secure access control
mechanisms, but it is also difficult to ensure these mechanisms are practical. My thesis addresses these
concerns. 

%\vspace{.3in}
%
%\noindent {\bf \sc Supervision Agreement:}
%
%\noindent The program outlined in this proposal is adequate for a Master of Science
%thesis.  The supplies and facilities required are available, and I am
%willing to supervise the research and evaluate the thesis report.
%\vspace{.3in}

%\begin{flushright}
%\begin{tabular}{@{}l}
%\brule{3.5in} \\
%Nickolai Zeldovich \\
%{\small Associate Professor, Parallel and Distributed Operating Systems Group} \\
%{\small MIT Computer Science and Artificial Intelligence Laboratory}
%
%
%\end{tabular}
%\end{flushright}
